Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-10-31 paper.tex
update

\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we model comprehensive quality awareness automated semantic service composition with graphs. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will propose a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with the five steps included. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in functional and non-functional parts. The first functional one is defined as $F(T_{Input}, T_{Output})$ , and the second nonfunctional one is users' accepted level of QoS. Step 2: Those requirements are initially used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space. Step 3: a graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered and connected while calculating matchmaking quality that will be explained in Subsect. \ref{qualityModel}. Step 4,5: The selection of web services is performed over the PSO algorithm in subSect. \ref{pso_algorithm}, which is used to find best particle location mapped back to a service queue for building graph solutions considering comprehensive quality. This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.
\subsection{Semantic matchmaking} \label{semantic_matchmaking}

The semantic matchmaking transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match: $match(C_{2}, C_{3})$ defined in Section \ref{semantic Web service Discovery}. The matching mechanism attempts to determine whether correct match criteria between the source concepts of C1 and the target concepts of C2, and the quality of semantic matchmaking for these two concepts is calculated in the quality model in subSection \ref{qualityModel}. The advantage of semantic matchmaking quality is to find a more closely requested service output with acceptable level of QoS.

@@

>>>>

\section{QoS-aware Semantic Automated Web Service Composition}\label{qswsc_approach}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{overview.pdf}}}
 \caption{Overview of the proposed approach.}
 \label{overview}
\end{figure}
In this paper, we model comprehensive quality awareness automated semantic service composition with graphs. PSO has shown its efficiency in solving combinatorial optimisation problems. Therefore, we will propose a PSO-based approach, which is considered to be simple and efficient without penalising or repairing comparing to GP \cite{da2014graph}. Fig. \ref{overview} shows the overview of our approach with the five steps included. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements in functional and non-functional parts. The first functional one is defined as $F(T_{Input}, T_{Output})$ , and the second nonfunctional one is users' accepted level of QoS. Step 2: Those requirements are initially used to discover all relevant web services, which leads to a shrunken service repository that further used by PSO as a searching space. Step 3: a graph representation is randomly built up interleaving with semantic matchmaking process, where web services are discovered and connected while calculating matchmaking quality that will be explained in Subsect. \ref{qualityModel}. Step 4,5: The selection of web services is performed over the PSO algorithm in subSect. \ref{pso_algorithm}, which is used to find best particle location mapped back to a service queue for building graph solutions considering comprehensive quality. This approach \cite{da2016particle} is an indirect representation of web service composition using PSO.

\subsection{Semantic matchmaking} \label{semantic_matchmaking}
To perform semantic matchmaking transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match in \ref{semantic Web service Discovery}. The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$ calculated in the quality model in subSection \ref{qualityModel}. The advantage of semantic matchmaking quality is to find a more closely requested service output with acceptable level of QoS.

@@

\subsection{Ontology-based Index Cache}
In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively. To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality and mark the input-parameter concepts with a set of services. The key idea of the index is to create a mapping from the output-related concepts to matched input-related services while considering different levels of match types. Furthermore, the repository size could also be reduced by considering users' predefined acceptable semantic matching quality, which eliminates the influence of low composition accuracy.  The service repository size is further reduced to the available output parameter concepts are input-relevant and more than the threshold.

This implementation contributes to less time and constant time for weighted graph building.
